A comparison between the latest Prophet forecasting model and the ARIMA model: An evaluation of BTC/ZAR predictability

### 2017-10-27 Draft/Write-up/Draft.Rmd
Gaah! Typos fixed

## Model Confidence Set
The Model Confidence Set (MCS) procedure developed by @hansen2011 is a sequential procedure which starts with an initial set of models $M_0$ of size m. The worse model is then eliminated at each step until the null hypothesis of equal predictive ability (EPA) fails to be rejected for all the models belonging to the set at a given confidence level $1 - \alpha$. This smaller set of models $M^*$ is the superior set of models (SSM) with the best case occurring when the SSM consists of a single best model.

@@

where $\mu_i,_j = E[d_i,_j]$ represents the expected loss differential, $d_i,_j,_t = l_i,_t - l_j,_t$ represents the loss differential between models $i$ and $j$ at time t, and $l_i,_t$ and $l_j,_t$ are the loss functions associated with model $i$ and $j$ at time t respectively. This paper makes use of the squared forecast error as a loss function, however any arbitrary loss function that satisfies the weak stationarity conditions described in @hansen2011 may be used.  
The null hypothesis is tested by constructing the following test statistics:

$$t_i,_j = \frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}$$ \vspace{1pt}
$$ T_R = \max_{i,j\in M} \;\; |t_i,_j|$$
where $d_i,_j = m^{-1}\sum_{t=1}^{m}{d_i,_j,_t }$ measures the sample average loss differential between model $i$ and $j$ and  $\hat{var[\bar{d_i,_j}]}$ is estimated through bootstrapping as described in @hansen2011.

This paper uses a block–bootstrap procedure of 5000 resamples as in @hansen2011. The block length $p$ is chosen by fitting an AR(p) model to the $d_i,_j$ terms and determining the maximum number of significant AR parameters obtained. While $t_i,_j$ has a t-distribution, $T_R$ has a non-standard distribution under the null hypothesis hence is estimated by implementing a bootstrapping procedure similar to that used to estimate $\hat{var[\bar{d_i,_j}]}$.

>>>>

## Model Confidence Set
The Model Confidence Set (MCS) procedure developed by @hansen2011 is a sequential procedure which starts with an initial set of models $M_0$ of size m. The worst model is then eliminated at each step until the null hypothesis of equal predictive ability (EPA) fails to be rejected for all the models belonging to the set at a given confidence level $1 - \alpha$. This smaller set of models $M^*$ is the superior set of models (SSM) with the best case occurring when the SSM consists of a single best model.

@@

where $\mu_i,_j = E[d_i,_j,_t]$ represents the expected loss differential, $d_i,_j,_t = l_i,_t - l_j,_t$ represents the loss differential between models $i$ and $j$ at time t, and $l_i,_t$ and $l_j,_t$ are the loss functions associated with model $i$ and $j$ at time t respectively. This paper makes use of the squared forecast error as a loss function, however any arbitrary loss function that satisfies the weak stationarity conditions described in @hansen2011 may be used.  
The null hypothesis is tested by constructing the following test statistics:

$$t_i,_j = \frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}$$ \vspace{1pt}
$$ T_R = \max_{i,j\in M} \;\; |t_i,_j|$$
where $\bar{d_i,_j} = m^{-1}\sum_{t=1}^{m}{d_i,_j,_t }$ measures the sample average loss differential between model $i$ and $j$ and  $\hat{var[\bar{d_i,_j}]}$ is estimated through bootstrapping as described in @hansen2011.

This paper uses a block–bootstrap procedure of 5000 resamples as in @hansen2011. The block length $p$ is chosen by fitting an AR(p) model to the $d_i,_j,_t$ terms and determining the maximum number of significant AR parameters obtained. While $t_i,_j$ has a t-distribution, $T_R$ has a non-standard distribution under the null hypothesis hence is estimated by implementing a bootstrapping procedure similar to that used to estimate $\hat{var[\bar{d_i,_j}]}$.

### 2017-10-27 Draft/Write-up/Draft.tex
Gaah! Typos fixed

The Model Confidence Set (MCS) procedure developed by Hansen, Lunde, and
Nason (2011) is a sequential procedure which starts with an initial set
of models \(M_0\) of size m. The worse model is then eliminated at each
step until the null hypothesis of equal predictive ability (EPA) fails
to be rejected for all the models belonging to the set at a given
confidence level \(1 - \alpha\). This smaller set of models \(M^*\) is
the superior set of models (SSM) with the best case occurring when the
SSM consists of a single best model.

@@

where \(\mu_i,_j = E[d_i,_j]\) represents the expected loss
differential, \(d_i,_j,_t = l_i,_t - l_j,_t\) represents the loss
differential between models \(i\) and \(j\) at time t, and \(l_i,_t\)
and \(l_j,_t\) are the loss functions associated with model \(i\) and
\(j\) at time t respectively. This paper makes use of the squared
forecast error as a loss function, however any arbitrary loss function
that satisfies the weak stationarity conditions described in Hansen,
Lunde, and Nason (2011) may be used.\\
The null hypothesis is tested by constructing the following test
statistics:

\[t_i,_j = \frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\]
\vspace{1pt} \[ T_R = \max_{i,j\in M} \;\; |t_i,_j|\] where
\(d_i,_j = m^{-1}\sum_{t=1}^{m}{d_i,_j,_t }\) measures the sample
average loss differential between model \(i\) and \(j\) and
\(\hat{var[\bar{d_i,_j}]}\) is estimated through bootstrapping as
described in Hansen, Lunde, and Nason (2011).

This paper uses a block--bootstrap procedure of 5000 resamples as in
Hansen, Lunde, and Nason (2011). The block length \(p\) is chosen by
fitting an AR(p) model to the \(d_i,_j\) terms and determining the
maximum number of significant AR parameters obtained. While \(t_i,_j\)
has a t-distribution, \(T_R\) has a non-standard distribution under the
null hypothesis hence is estimated by implementing a bootstrapping
procedure similar to that used to estimate \(\hat{var[\bar{d_i,_j}]}\).

>>>>

The Model Confidence Set (MCS) procedure developed by Hansen, Lunde, and
Nason (2011) is a sequential procedure which starts with an initial set
of models \(M_0\) of size m. The worst model is then eliminated at each
step until the null hypothesis of equal predictive ability (EPA) fails
to be rejected for all the models belonging to the set at a given
confidence level \(1 - \alpha\). This smaller set of models \(M^*\) is
the superior set of models (SSM) with the best case occurring when the
SSM consists of a single best model.

@@

where \(\mu_i,_j = E[d_i,_j,_t]\) represents the expected loss
differential, \(d_i,_j,_t = l_i,_t - l_j,_t\) represents the loss
differential between models \(i\) and \(j\) at time t, and \(l_i,_t\)
and \(l_j,_t\) are the loss functions associated with model \(i\) and
\(j\) at time t respectively. This paper makes use of the squared
forecast error as a loss function, however any arbitrary loss function
that satisfies the weak stationarity conditions described in Hansen,
Lunde, and Nason (2011) may be used.\\
The null hypothesis is tested by constructing the following test
statistics:

\[t_i,_j = \frac{\bar{d_i,_j}}{\sqrt{\hat{var[\bar{d_i,_j}]}}}\]
\vspace{1pt} \[ T_R = \max_{i,j\in M} \;\; |t_i,_j|\] where
\(\bar{d_i,_j} = m^{-1}\sum_{t=1}^{m}{d_i,_j,_t }\) measures the sample
average loss differential between model \(i\) and \(j\) and
\(\hat{var[\bar{d_i,_j}]}\) is estimated through bootstrapping as
described in Hansen, Lunde, and Nason (2011).

This paper uses a block--bootstrap procedure of 5000 resamples as in
Hansen, Lunde, and Nason (2011). The block length \(p\) is chosen by
fitting an AR(p) model to the \(d_i,_j,_t\) terms and determining the
maximum number of significant AR parameters obtained. While \(t_i,_j\)
has a t-distribution, \(T_R\) has a non-standard distribution under the
null hypothesis hence is estimated by implementing a bootstrapping
procedure similar to that used to estimate \(\hat{var[\bar{d_i,_j}]}\).
